\documentclass[../Main.tex]{subfiles}
\pagenumbering{roman}
\begin{document}
	\begin{center}
		\Large{\textbf{ACKNOWLEDGMENTS}}\\
	\end{center}
	\vspace{1cm}
	In completing this bachelor's thesis, titled "The Impact of University-Based Incubation Programs on Startup Performance: A Multi-Factor Analysis", I have been fortunate to receive invaluable support, guidance, and assistance from many individuals.

	First and foremost, I would like to express my sincere gratitude to my supervisor, Assoc. Prof. Dr. Nguyen Thi Thanh Thuy. Her expert guidance and critical feedback were invaluable in shaping the direction of this thesis.

	I also wish to extend my sincere thanks to the esteemed faculty and staff of the School of Economics and Management at Hanoi University of Science and Technology. The knowledge and skills I acquired during my studies in the Business Analytics program provided me with the necessary tools to undertake this research.

	To develop a research framework and survey instruments that are relevant to the practical context, I received invaluable advice and feedback from several experts and senior professionals in the entrepreneurial ecosystem. I am truly grateful for their critical insights and guidance. I also recognize that the future success of this thesis will heavily depend on the willing participation of the founders, managers, and mentors who will contribute their time and knowledge. I wish to express my gratitude in advance for their anticipated contributions, which will form the very core of this research.

	Finally, and most importantly, I owe my deepest gratitude to my beloved family. To my parents, thank you for your unconditional love, unwavering faith in me, and the immense sacrifices you have made for my education. This accomplishment would not have been possible without you.

	Once again, I extend my sincere thanks to all who have supported me on this academic journey.
\end{document}